---
title: "Geog533 Lab 8"
author: "Frank Tolbert"
output:
  html_document:
    toc: yes
  html_notebook:
    toc: yes
    toc_float: yes
---

Complete the following exercises in Chapter 8 (Introduction to Regression Analysis) of the textbook [R] pages 247-250. 

## Question 1

This is Exercise 1 in Chapter 8 of the Textbook [R].

A regression of weekly shopping trip frequency on annual income (data entered in thousands of dollars) is performed on data collected from 24 respondents. The results are summarized below:

* Intercept: 0.46
* Slope: 0.19

|          | Sum of squares  | Degrees of freedom |  Mean square   |       *F*       |
|----------|-----------------|--------------------|----------------|-----------------|
|Regression|                 |                    |                |                 |
| Residual |       1.7       |                    |                |                 |
| Total    |       2.3       |                    |                |                 |
|          | Sum of squares  | Degrees of freedom |  Mean square   |       *F*       |


### Question 1(a)
Fill in the blanks in the ANOVA table.

```{r}
N <- 24
resSS <- .6
resDF <- N-2 
totalDF <- N-1
resMS <- 1.7/resDF
resMSs <- round(resMS, 3)
F <- round(resSS/resMS, 2)

```


|          | Sum of squares  | Degrees of freedom |  Mean square   |       *F*       |
|----------|-----------------|--------------------|----------------|-----------------|
|Regression|       `r resSS` |        1           |     `r resSS`/1|.6(1.7/`r resDF`)|
| Residual |       1.7       |       `r resDF`    | `r resMSs`     |                 |
| Total    |       2.3       |        `r totalDF` |    `           |                 |

### Question 1(b)
What is the predicted number of weekly shopping trips for someone making $50,000/year?
```{r}
predicted <- 0.46 + 50*0.19
predicted
```


### Question 1(c)
In words, what is the meaning of the coefficient 0.19?

###Solution1c
$1 in Income = 0.19 Shopping Trips

### Question 1(d)
Is the regression coefficient significantly different from zero? How do you know?
```{r}
critical1 <- qf(.95,1,22)
if(F < critical1){
print("we fail to reject the null")
} else {
print("We reject the null hypothesis, because the F value > F.Critical")}

#Coefficient is Significantly Different than Zero
```



### Question 1(e)
What is the value of the correlation coefficient?
```{r}
R <- sqrt(resSS/2.3)
round(R,3)
```





## Question 2

This is Exercise 6 in Chapter 8 of the Textbook [R].

The following data are collected in an effort to determine whether snowfall is dependent upon elevation: 

| Snowfall (inches) | Elevation (feet) |
|-------------------|------------------|
|       36          |       400        |
|       78          |       800        |
|       11          |       200        |
|       45          |       675        |

Using R, show your work on exercises (a) through (g).

### Question 2(a)
Find the regression coefficients (the intercept and the slope coefficient).
```{r}

x <- c(36, 78, 11, 45)

y <- c(400, 800 ,200 ,675)

m <- lm(y~x)

result <- summary(m)

result
#INTERCEPT: 127.412
#Slope Coef: 9.208
```


### Question 2(b)
Estimate the standard error of the residuals about the regression line.
```{r}
#InPreviousQuestion: 109.8
```


### Question 2(c)
Test the hypothesis that the regression coefficient associated with the independent variables is equal to zero. Also place a 95% confidence interval on the regression coefficient.
```{r}
F2.0 <- 16.7
critical2.0 <- qf(.95, 1, 2)
if(F2.0 < critical2.0){
print("fail to reject the null hypothesis, the regression coefficient is not equal to zero")
} else {
print("we reject the null hypothesis")}
se <- 2.29
q95 <- qnorm(0.975)
conf95 <- c(F2.0-q95*se, F2.0+q95*se)
conf95
```


### Question 2(d)
Find the value of $r^2$.
```{r}
testing <- cor.test(y,x, method = "pearson")
r2 <- testing$estimate^2
round(r2, 3)
```


### Question 2(e)
Make a table of the observed values, predicted values, and the residuals.
```{r}
table <- data.frame(x,y)
table$predicted <- round(m$fitted.values,2)
table$residuals <- round(m$residuals,2)
names(table) <- c("Snowfall (Inches)", "Elevation (Feet)", "Predicted Values", "Residuals")
library(knitr)
kable(table)

```


### Question 2(f)
Prepare an analysis of variance table portraying the regression results.
```{r}
anova(m)
```


|          | Sum of squares  | Degrees of freedom |  Mean square   |       *F*       |
|----------|-----------------|--------------------|----------------|-----------------|
|Regression|    195094       |          1         |    195094      |       16.173    |
| Residual |     24125       |           2        |      12063     |                 |
| Total    |      219219     |          3         |                |                 |

### Question 2(g)
Graph the data and the regression line.
```{r}
plot(y~x)
abline(m,col='red',lwd=2)
segments(x,predicted,x,y,col='blue',lty="dashed")
```




## Question 3

This is Exercise 10 in Chapter 8 of the Textbook [R].

Use R and the [Milwaukee dataset](http://spatial.binghamton.edu/geog533/data/Milwaukee_Sales.csv) to:

### Problem
perform a regression using sales price as the dependent variable and lot size as the independent variable.

### Solution
```{r}
df <- read.csv("http://spatial.binghamton.edu/geog533/data/Milwaukee_Sales.csv")
x2 <- df$LotSize
y2 <- df$SalePrice
m <- lm(y2~x2)
summary(m)
perform <- plot(y2~x2)
abline(m,col='red',lwd=2)
segments(x2,predicted,x2,y2,col='blue',lty="dashed")

```



## Question 4

This is Exercise 11 in Chapter 8 of the Textbook [R].

Use R and the Hypothetical [UK Housing Prices dataset](http://spatial.binghamton.edu/geog533/data/UK_Housing.csv) to:

### Question 4(a) 
perform a regression using house price as the dependent variable, and number of bedrooms as the independent variable;

```{r}
df <- read.csv("http://spatial.binghamton.edu/geog533/data/UK_Housing.csv")
x3 <- df$bedrooms
y3 <- df$price
m <- lm(y3~x3)
summary(m)
perform2 <- plot(y3~x3)
abline(m,col='red',lwd=2)
segments(x3,predicted,x3,y3,col='blue',lty="dashed")

```


### Question 4(b) 
(b) repeat part (a), using the number of bathrooms as the independent variable, and comment on the results.
```{r}
df <- read.csv("http://spatial.binghamton.edu/geog533/data/UK_Housing.csv")
x4 <- df$bathrooms
y4 <- df$price
m <- lm(y4~x4)
perform3 <- plot(y4~x4)
abline(m,col='red',lwd=2)
segments(x4,predicted,x4,y4,col='blue',lty="dashed")


#As housing prices increases, the number bedrooms and bathrooms increase.
```


## Question 5
Download the [hometown.csv](http://spatial.binghamton.edu/geog533/data/hometown.csv), append your name and hometown coordinates to the csv, then use [leaflet](https://rstudio.github.io/leaflet/) to create a web map (10 pt.)

```{r}
library(leaflet)
m <- leaflet()
m <- addTiles(m)
m <- addMarkers(m, lng=-73.7949, lat=41.1220, popup="Westchester County")
m
```
