---
title: "Geog533 Lab 10"
author: "Frank Tolbert"
output:
  html_document:
    toc: yes
  html_notebook:
    toc: yes
    toc_float: yes
---

## Question 1
Use R package UScensus2010county to complete the following tasks:  (20 pt.)

### Question 1(a)
Plot a map of New York counties using the plot function.
```{r}
library(UScensus2010)
if(!require(UScensus2010county)) install.county("osx")
library(UScensus2010county)
data(new_york.county10)
shp <- new_york.county10
plot(shp)
```

### Question 1(b)	
Plot a map of New York counties using the qtm function.
```{r}
library(tmap)
qtm(shp)
```


### Question 1(c)	
How many counties in New York State?
```{r}
NROW(shp)
print("62 counties in NY")
```

### Question 1(d)	
What’s the 3-digit fips code of Broome County?
```{r}
shp[shp$NAME10 == "Broome",]
print("Broome County Fips: 007")
```

### Question 1(e)	
Compute descriptive statistics of the population column (P0010001), including total, minimum, maximum, mean, median, and skewness. 
```{r}
populate <- shp@data

min(populate$P0010001)

max(populate$P0010001)

mean(populate$P0010001)

median(populate$P0010001)

library(e1071)
skewness(populate$P0010001)
```

### Question 1(f)	
Create a histogram and a boxplot of the population.
```{r}
hist(shp$P0010001, main="NYS Population Histogram")

boxplot(shp$P0010001, main="NYS Population Boxplot")
```


## Question 2
Use R package UScensus2010tract to complete the following tasks:    (20 pt.)
```{r}

```

### Question 2(a)	
Plot a map of New York census tracts using the plot function.
```{r}
library(UScensus2010tract)
data("new_york.tract10")
tract <- new_york.tract10
plot(tract)
```

### Question 2(b)
Compute the total population based on census tracts.
```{r}
poptracts <- tract@data
sum(poptracts$P0010001)
```

### Question 2(c)
Select all census tracts in Broome County and plot the map. 
```{r}
library(UScensus2010)
BC <- county(fips="007",name="Broome",state="NY",level="tract")
plot(BC)
```

### Question 2(d)
What’s the total population of Broome County?
```{r}
BCpop <- sum(BC$P0010001)
BCpop
```

### Question 2(e)
Create a histogram and a boxplot of population based on census tracts of Broome County.
```{r}
hist(BC$P0010001,main="Broome County Population Histogram")

boxplot(BC$P0010001,main="Broome County Population Boxplot")
```

### Question 2(f)
Select the first five columns of the shapefile of Broome County census tract; add a new population ratio column (= census tract population / county population); save the new shapefile to the hard drive. 
```{r}
poprat <- data.frame(BC[,1:5])
poprat$ratio <- BC$P0010001/200600
poprat
```


## Question 3

Use R packages raster and ncdf4 to complete the following tasks:     (20 pt.)
```{r}
library(raster)
library(ncdf4)
```

### Question 3(a)		
Load the multi-band raster dataset “NDVI.nc” into R.
```{r}
ndvi <- brick("NDVI.nc")
ndvi
```

### Question 3(b)		
Get the basic information about the dataset, including the number of rows, columns, cells, and bands; spatial resolution, extent, bounding box, and projection.
```{r}
nrow(ndvi)
ncol(ndvi)
ncell(ndvi)
nbands(ndvi)
res(ndvi)
extent(ndvi)
bbox(ndvi)
projection(ndvi)
```

### Question 3(c)	
Aggregate all bands to generate a mean NDVI raster and a maximum NDVI raster; save the two new raster datasets to the hard drive. 
```{r}
mean(ndvi)
writeRaster(mean(ndvi),filename = "mean_ndvi.tif", overwrite=TRUE)
max(ndvi)
writeRaster(max(ndvi),filename = "max_ndvi.tif", overwrite=TRUE)
```

### Question 3(d)			
Plot the maps of monthly NDVI of the year 2001
```{r}
m2001 <- ndvi[[13:24]]
plot(m2001)
```

### Question 3(e)	
Create histograms of monthly NDVI of the year 2001.
```{r}
hist(m2001)
```

### Question 3(f)			
Plot the NDVI map of July 2000; click any location with data on the map and retrieve the NDVI time series for all years; plot the NDVI time series of the selected location. 
```{r}
plot(ndvi[[7]])
values <- ndvi[150, 50]
```

